---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(readr)
library(ggpubr)
library(psych)


TransNudge_ <- read_csv("~/Desktop/Jordan Capstone_April 14, 2022_08.16.csv")
```

```{r}
TransNudgeFinal <- TransNudge_ %>% 
  filter(`Attention Check 1` == 9) %>%
  mutate(Donation_Cont = ((as.numeric(`Donation Control`) - 1) / 2)) %>%
  select(`Donation_Cont`,
         `Donation Transparent_1`,
         `Donation Opaque_1`,
         `Autonomy 1`,
         `Autonomy 2`,
         `Autonomy 3`,
         `Attention Check 1`,
         `Autonomy 4`,
         `Freedom 1`,
         `Freedom 2`,
         `Freedom 3`,
         `Freedom 4`,
         `Agreement`,
         `Gender`,
         `Age`,
         `Race/ethnicity`) 

```

```{r}
#data cleaning
TransNudgeFinal2 <- TransNudgeFinal %>% 
    #NAs in Agreement are 4
  mutate_at(vars("Agreement"), ~replace_na(.,3)) %>%
  mutate(donation = case_when(!is.na(Donation_Cont) ~ Donation_Cont,
                              !is.na(as.numeric(`Donation Transparent_1`)) ~ as.numeric(`Donation Transparent_1`),
                              !is.na(as.numeric(`Donation Opaque_1`)) ~ as.numeric(`Donation Opaque_1`)),
         treatment = case_when(!is.na(Donation_Cont) ~ 0,
                              !is.na(as.numeric(`Donation Transparent_1`)) ~ 1,
                              !is.na(as.numeric(`Donation Opaque_1`)) ~ 2),
         overall_freedom = (as.numeric(`Freedom 1`) + as.numeric(`Freedom 2`) + as.numeric(`Freedom 3`) + as.numeric(`Freedom 4`)),
         avg_freedom = (10 - (overall_freedom/4)),
        overall_autonomy = (as.numeric(`Autonomy 1`) + as.numeric(`Autonomy 2`) + as.numeric(`Autonomy 3`) + as.numeric(`Autonomy 4`)),
        avg_autonomy = (overall_autonomy/4),
        freedom_score = ((avg_freedom + avg_autonomy)/2),
        agreement = (as.numeric(Agreement)),
        white = (as.numeric(`Race/ethnicity`) != 2),
        young = (as.numeric(`Age`) <= 24))


#Treatment: 0 = control, 1 = trans, 2 = trad
#Agreement: 0 = agree, 1 = disagree, 2 = neither agree nor disagree, 3 = na (control)
```


Hypotheses 1 & 2: Treatment on donation

```{r}
#kruskal-wallis comparing donations by treatment
kruskal.test(donation ~ treatment, data = TransNudgeFinal2)
```

```{r}
#wilcox comparing donations by treatment 1v1

#trans vs trad
TransNudgeFinal2 %>% 
  filter(treatment != 0) %>% 
  wilcox.test(donation ~ treatment, data = .) 

#control vs trad
TransNudgeFinal2 %>% 
  filter(treatment != 1) %>% 
  wilcox.test(donation ~ treatment, data = .) 

#control vs trans
TransNudgeFinal2 %>% 
  filter(treatment != 2) %>% 
  wilcox.test(donation ~ treatment, data = .) 
```

```{r}
#cohen D power of how treatment predicts donation

#trans vs. trad
TransNudgeFinal2 %>% 
  filter(treatment != 0) %>% 
  cohen.d(donation ~ treatment, data = .) 

#control vs. trad
TransNudgeFinal2 %>% 
  filter(treatment != 1) %>% 
  cohen.d(donation ~ treatment, data = .) 

#trans vs. control
TransNudgeFinal2 %>% 
  filter(treatment != 2) %>% 
  cohen.d(donation ~ treatment, data = .) 
```


Hypothesis 3: Agreement on donation

```{r}
#kruskal-wallis comparing donations by agreement
Hyp3 <- TransNudgeFinal2 %>% filter (agreement != 3)
kruskal.test(donation ~ agreement, data = Hyp3)
```

```{r}
#wilcox comparing donations by agreement 1v1

#Disagree vs. Neutral
Hyp3 %>% 
  filter(agreement != 0) %>% 
  wilcox.test(donation ~ agreement, data = .) 

#Agree vs. Neutral
Hyp3 %>% 
  filter(agreement != 1) %>% 
  wilcox.test(donation ~ agreement, data = .) 

#Agree vs. Disagree
Hyp3 %>% 
  filter(agreement != 2) %>% 
  wilcox.test(donation ~ agreement, data = .) 
```

```{r}
#cohen D power of how agreement predicts donation

#Disagree vs. Neutral
Hyp3 %>% 
  filter(agreement != 0) %>% 
  cohen.d(donation ~ agreement, data = .) 

#Agree vs. Neutral
Hyp3 %>% 
  filter(agreement != 1) %>% 
  cohen.d(donation ~ agreement, data = .) 

#Agree vs. Disagree
Hyp3 %>% 
  filter(agreement != 2) %>% 
  cohen.d(donation ~ agreement, data = .) 

```


Hypotheses 4 & 5: Treatment on freedom

```{r}
#kruskal-wallis comparing freedom by treatment
kruskal.test(freedom_score ~ treatment, data = TransNudgeFinal2)
```

```{r}
#wilcox comparing freedom by treatment 1v1

#trans vs trad
TransNudgeFinal2 %>% 
  filter(treatment != 0) %>% 
  wilcox.test(freedom_score ~ treatment, data = .) 

#control vs trad
TransNudgeFinal2 %>% 
  filter(treatment != 1) %>% 
  wilcox.test(freedom_score ~ treatment, data = .) 

#control vs trans
TransNudgeFinal2 %>% 
  filter(treatment != 2) %>% 
  wilcox.test(freedom_score ~ treatment, data = .) 
```

```{r}
#cohen D power of how treatment predicts freedom

#trans vs. trad
TransNudgeFinal2 %>% 
  filter(treatment != 0) %>% 
  cohen.d(freedom_score ~ treatment, data = .) 

#control vs. trad
TransNudgeFinal2 %>% 
  filter(treatment != 1) %>% 
  cohen.d(freedom_score ~ treatment, data = .) 

#trans vs. control
TransNudgeFinal2 %>% 
  filter(treatment != 2) %>% 
  cohen.d(freedom_score ~ treatment, data = .) 
```


Hypothesis 6: Agreement on freedom

```{r}
#kruskal-wallis comparing freedom by agreement
Hyp3 <- TransNudgeFinal2 %>% filter (agreement != 3)
kruskal.test(freedom_score ~ agreement, data = Hyp3)
```

```{r}
#wilcox comparing freedom by agreement 1v1

#Disagree vs. Neutral
Hyp3 %>% 
  filter(agreement != 0) %>% 
  wilcox.test(freedom_score ~ agreement, data = .) 

#Agree vs. Neutral
Hyp3 %>% 
  filter(agreement != 1) %>% 
  wilcox.test(freedom_score ~ agreement, data = .) 

#Agree vs. Disagree
Hyp3 %>% 
  filter(agreement != 2) %>% 
  wilcox.test(freedom_score ~ agreement, data = .) 
```

```{r}
#cohen D power of how agreement predicts freedom

#Disagree vs. Neutral
Hyp3 %>% 
  filter(agreement != 0) %>% 
  cohen.d(freedom_score ~ agreement, data = .) 

#Agree vs. Neutral
Hyp3 %>% 
  filter(agreement != 1) %>% 
  cohen.d(freedom_score ~ agreement, data = .) 

#Agree vs. Disagree
Hyp3 %>% 
  filter(agreement != 2) %>% 
  cohen.d(freedom_score ~ agreement, data = .) 

```


Exploratory analysis 1: freedom by condition within neutral agreement

```{r}
#wilcox comparing freedom by treatment within neutral 1v1

neutral <- TransNudgeFinal2 %>% filter(agreement == 2) 

#trans vs. trad
neutral %>% 
  wilcox.test(freedom_score ~ treatment, data = .) 
```

```{r}
#cohen D power of how treatment predicts freedom with neutral

#trans vs. trad
neutral %>% 
  cohen.d(freedom_score ~ treatment, data = .) 

```


Exploratory analysis 2: donation by condition within neutral agreement

```{r}
#wilcox comparing donation by treatment within neutral 1v1

#trans vs. trad
neutral %>% 
  wilcox.test(donation ~ treatment, data = .) 
```

```{r}
#cohen D power of how treatment predicts freedom with neutral

#trans vs. trad
neutral %>% 
  cohen.d(donation ~ treatment, data = .) 

```


Exploratory Analysis 3: Agreement on donation within Trans condition

```{r}
#kruskal-wallis comparing donations by agreement within trans cond
Transcond <- TransNudgeFinal2 %>% filter(treatment == 1) %>% filter(agreement !=3)

kruskal.test(donation ~ agreement, data = Transcond)
```

```{r}
#wilcox comparing donations by agreement within trans cond 1v1

#disagree vs neutral
Transcond %>% 
  filter(agreement != 0) %>% 
  wilcox.test(donation ~ agreement, data = .) 

#agree vs neutral
Transcond %>% 
  filter(agreement != 1) %>% 
  wilcox.test(donation ~ agreement, data = .) 

#agree vs disagree
Transcond %>% 
  filter(agreement != 2) %>% 
  wilcox.test(donation ~ agreement, data = .) 
```

```{r}
#cohen D power of how agreement predicts donation with transcond

#disagree vs. neutral
Transcond %>% 
  filter(agreement != 0) %>% 
  cohen.d(donation ~ agreement, data = .) 

#agree vs. neutral
Transcond %>% 
  filter(agreement != 1) %>% 
  cohen.d(donation ~ agreement, data = .) 

#agree vs. disagree
Transcond %>% 
  filter(agreement != 2) %>% 
  cohen.d(donation ~ agreement, data = .) 
```


Exploratory Analysis 4: Agreement on freedom within Trans condition

```{r}
#kruskal-wallis comparing freedom by agreement
Transcond <- TransNudgeFinal2 %>% filter(treatment == 1) %>% filter(agreement !=3)

kruskal.test(freedom_score ~ agreement, data = Transcond)
```

```{r}
#wilcox comparing freedom by agreement within trans cond 1v1

#disagree vs neutral
Transcond %>% 
  filter(agreement != 0) %>% 
  wilcox.test(freedom_score ~ agreement, data = .) 

#agree vs neutral
Transcond %>% 
  filter(agreement != 1) %>% 
  wilcox.test(freedom_score ~ agreement, data = .) 

#agree vs disagree
Transcond %>% 
  filter(agreement != 2) %>% 
  wilcox.test(freedom_score ~ agreement, data = .) 
```

```{r}
#cohen D power of how agreement predicts freedom with transcond

#disagree vs. neutral
Transcond %>% 
  filter(agreement != 0) %>% 
  cohen.d(freedom_score ~ agreement, data = .) 

#agree vs. neutral
Transcond %>% 
  filter(agreement != 1) %>% 
  cohen.d(freedom_score ~ agreement, data = .) 

#agree vs. disagree
Transcond %>% 
  filter(agreement != 2) %>% 
  cohen.d(freedom_score ~ agreement, data = .) 
```


Demographic Analyses

```{r}
#Race/ethnicity
#donation
TransNudgeFinal2 %>% 
  wilcox.test(donation ~ white, data = .) 
#freedom
TransNudgeFinal2 %>% 
  wilcox.test(freedom_score ~ white, data = .) 

#Gender
#donation
TransNudgeFinal2 %>% 
  wilcox.test(donation ~ Gender, data = .) 
#freedom
TransNudgeFinal2 %>% 
  wilcox.test(freedom_score ~ Gender, data = .) 

#Age
#donation
TransNudgeFinal2 %>% 
  wilcox.test(donation ~ young, data = .) 
#freedom
TransNudgeFinal2 %>% 
  wilcox.test(freedom_score ~ young, data = .) 
```


Some Summary Stats

```{r}

#average donation by treatment
 #control
      TransNudgeFinal2 %>%   
      filter(treatment == 0) %>%
        summarize(min = min(donation),
          count = n(),
          median = median(donation),
          mean = mean(donation))
#trans
      TransNudgeFinal2 %>%   
      filter(treatment == 1) %>%
        summarize(min = min(donation),
          count = n(),
          median = median(donation),
          mean = mean(donation))
#trad
            TransNudgeFinal2 %>%   
      filter(treatment == 2) %>%
        summarize(min = min(donation),
          count = n(),
          median = median(donation),
          mean = mean(donation))
            
#average donation by agreement
#agree
      TransNudgeFinal2 %>%   
      filter(agreement == 0) %>%
        summarize(min = min(donation),
          count = n(),
          median = median(donation),
          mean = mean(donation))
#disagree
      TransNudgeFinal2 %>%   
      filter(agreement == 1) %>%
        summarize(min = min(donation),
          count = n(),
          median = median(donation),
          mean = mean(donation))
#neutral
            TransNudgeFinal2 %>%   
      filter(agreement == 2) %>%
        summarize(min = min(donation),
          count = n(),
          median = median(donation),
          mean = mean(donation))
            
#average freedom by treatment
#control
      TransNudgeFinal2 %>%   
      filter(treatment == 0) %>%
        summarize(min = min(freedom_score),
          count = n(),
          median = median(freedom_score),
          mean = mean(freedom_score))
#trans
      TransNudgeFinal2 %>%   
      filter(treatment == 1) %>%
        summarize(min = min(freedom_score),
          count = n(),
          median = median(freedom_score),
          mean = mean(freedom_score))
#trad
            TransNudgeFinal2 %>%   
      filter(treatment == 2) %>%
        summarize(min = min(freedom_score),
          count = n(),
          median = median(freedom_score),
          mean = mean(freedom_score))
            
#average freedom by agreement
#agree
      TransNudgeFinal2 %>%   
      filter(agreement == 0) %>%
        summarize(min = min(freedom_score),
          count = n(),
          median = median(freedom_score),
          mean = mean(freedom_score))
#disagree
      TransNudgeFinal2 %>%   
      filter(agreement == 1) %>%
        summarize(min = min(freedom_score),
          count = n(),
          median = median(freedom_score),
          mean = mean(freedom_score))
#neutral
            TransNudgeFinal2 %>%   
      filter(agreement == 2) %>%
        summarize(min = min(freedom_score),
          count = n(),
          median = median(freedom_score),
          mean = mean(freedom_score))
            
```



Data visualizations

Hypotheses 1 & 2: donation by treatment

```{r}

#visualization for donation comparison by treatment

my_comparisons <- list( c("0", "1"), c("1", "2"), c("0", "2") )


TransNudgeFinal2 %>% 
  ggplot(aes(x = as.factor(treatment), y = donation)) +
  geom_boxplot() + 
  geom_jitter() +
  ylab("Donation") +
  xlab("Treatment") +
  scale_x_discrete(labels = c("Control", "Transparent", "Traditional")) +
  theme_classic() +
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 14)
```


Hypothesis 3: donation by agreement 

```{r}

#visualization for donation comparison by agreement

my_comparisons <- list( c("0", "1"), c("1", "2"), c("0", "2") )


Hyp3 %>% 
  ggplot(aes(x = as.factor(agreement), y = donation)) +
  geom_boxplot() + 
  geom_jitter() +
  ylab("Donation") +
  xlab("Agreement Type") +
  scale_x_discrete(labels = c("Agree", "Disagree", "Neutral")) +
  theme_classic() +
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 14)
```


Hypotheses 4 & 5: Treatment on freedom

```{r}

#visualization for freedom comparison by treatment 

my_comparisons <- list( c("0", "1"), c("1", "2"), c("0", "2") )


TransNudgeFinal2 %>% 
  ggplot(aes(x = as.factor(treatment), y = freedom_score)) +
  geom_boxplot() + 
  geom_jitter() +
  ylab("Average Perceived Freedom Score") +
  xlab("Treatment") +
  scale_x_discrete(labels = c("Control", "Transparent", "Traditional")) +
  theme_classic() +
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 14)
```


Hypothesis 6: Agreement on freedom

```{r}

#visualization for freedom comparison by agreement 

my_comparisons <- list( c("0", "1"), c("1", "2"), c("0", "2") )


Hyp3 %>% 
  ggplot(aes(x = as.factor(agreement), y = freedom_score)) +
  geom_boxplot() + 
  geom_jitter() +
  ylab("Average Perceived Freedom Score") +
  xlab("Agreement Type") +
  scale_x_discrete(labels = c("Agree", "Disagree", "Neutral")) +
  theme_classic() +
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 15) + 
  scale_y_continuous(limits=c(0,15), breaks = c(0,5,10))
```


Exploratory Analysis 1: treatment on freedom within neutral

```{r}

#visualization for freedom comparison by treatment within neutral

my_comparisons <- list( c("0", "1"), c("1", "2"), c("0", "2") )


neutral %>% 
  ggplot(aes(x = as.factor(treatment), y = freedom_score)) +
  geom_boxplot() + 
  geom_jitter() +
  ylab("Average Perceived Freedom Score") +
  xlab("Treatment for those who felt neutral about the Salvation Army") +
  scale_x_discrete(labels = c("Transparent", "Traditional")) +
  theme_classic() +
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 12)
```


Exploratory Analysis 2: treatment on donation within neutral

```{r}

#visualization for freedom comparison by treatment within neutral

my_comparisons <- list( c("0", "1"), c("1", "2"), c("0", "2") )


neutral %>% 
  ggplot(aes(x = as.factor(treatment), y = donation)) +
  geom_boxplot() + 
  geom_jitter() +
  ylab("Donation") +
  xlab("Treatment for those who feel neutral about the Salvation Army") +
  scale_x_discrete(labels = c("Transparent", "Traditional")) +
  theme_classic() +
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 10)
```


Exploratory Analysis 3: Agreement on donation within Trans condition

```{r}

#visualization for donation comparison by agreement within trans condition

my_comparisons <- list( c("0", "1"), c("1", "2"), c("0", "2") )


Transcond %>% 
  ggplot(aes(x = as.factor(agreement), y = donation)) +
  geom_boxplot() + 
  geom_jitter() +
  ylab("Donation") +
  xlab("Agreement Type within Transparent Treatment") +
  scale_x_discrete(labels = c("Agree", "Disagree", "Neutral")) +
  theme_classic() +
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 14)
```


Exploratory Analysis 4: Agreement on freedom within Trans condition

```{r}

#visualization for freedom comparison by agreement within trans cond

my_comparisons <- list( c("0", "1"), c("1", "2"), c("0", "2") )


Transcond %>% 
  ggplot(aes(x = as.factor(agreement), y = freedom_score)) +
  geom_boxplot() + 
  geom_jitter() +
  ylab("Average Perceived Freedom Score") +
  xlab("Agreement Type within Transparent Treatment") +
  scale_x_discrete(labels = c("Agree", "Disagree", "Neutral")) +
  theme_classic() +
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 15)
```